First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/body.tex
updated

A 10.6005 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the SHMS and High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.
The beam currents delivered by the accelerator ranged between 40-60 $\mu$A due to frequent beam trips at higher currents and the beam was rastered over a 2x2 mm$^{2}$ area to reduce
the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\

@@

\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. In the high missing momentum settings the spectrometer configuration was changed
multiple times resulting in either the spectrometer angle or momentum not being excactly the same. As a result, two separate data sets were measured for the 580 MeV/c setting and three data sets for the 750 MeV/c setting.  
The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept ``fixed'' at ($\sim$12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to $\sim$(54.992 deg, 2.1925 GeV/c) and $\sim$(58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. \\
\indent At these kinematics, the 3-momentum transfer is $|\vec{q}| \sim 2.88$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$) measured on this experiment. As a result
one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$, $\theta_{pq}\sim 0$. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
neutron is struck while the detected proton is a spectator. FSIs are also expected to be largely reduced as compared to the ``perpendicular-kinematics'' in which the
proton is detected almost perpendicular to $\vec{q}$ based on a calculation by Arenh\"{o}vel on Table 1 of Ref.\cite{pr01-020}.\\
% (5) At these kinematics, the 3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred
%to the proton. As a result, the ejected proton scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$. This configuration is known as the ``parallel-kinematics'' and suppresses
%the process in which the neutron is struck and the proton is a spectator. \\
\indent In addition to deuteron kinematics,  $^{1}H(e,e'p)$ elastic data was also taken at kinematics close to the deuteron 80 MeV setting for cross-checks with the spectrometer acceptance model as well as for normalization purposes using the  Hall C Monte Carlo
simulation program, SIMC. Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics optimization, 
momentum calibration and determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\
\indent The event selection criteria was done exactly the same for the hydrogen and deuteron data. The criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the collimator edges, 3) a missing
energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a z-vertex difference cut between the HMS and SHMS $z$ reaction vertex difference to select events that truly

@@

\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption\cite{cyero_pAbs} and target boiling factors\cite{cyero_tgtBoil}.
For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
model. The data to SIMC yield ratio integrated over invariant mass $W$ was determined to be unity, so there was no need to include an overall hydrogen normalization factor. For the $^{2}H(e,e'p)n$ data,
the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. Variations
of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential. The 80 MeV data was also checked for reproducibility against the Hall A data (See Fig. \ref{fig:fig2}).
This agreement gives us confidence on the measurements made at higher missing momentum setting for which no previous data exists. \\
\indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made. Determination of systematics on these quantities is a work in progress. (Private communication with D. Mack)} and kinematic uncertainties. The individual contributions from normalization uncertainties
were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)

@@

\indent The kinematic uncertainties were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins

@@

The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature

@@

\indent The data was radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects. Bin-centering
corrections were also applied by multiplying the radiative corrected cross sections to the ratio of theoretical cross sections (external to SIMC) to the average cross sections calculated from SIMC.
The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. \\
\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were averaged for overlapping bins in $p_{r}$,
where the reduced cross sections are defined as follows:

@@

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using P. Bosted's form factor parametrization \cite{PhysRevC.51.409}.
Only within the PWIA, can $\sigma_{red}$ be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
cross section have been factored out by $\sigma_{cc1}$, leaving only a dependency on $p_{r}$. \\
\begin{figure}
\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M. Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
up to $\sim$ 800 MeV/c before being overwhelmed by FSIs. The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}], both the data and
CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
a similar behaviour as in Fig. \hyperref[fig:fig1]{1(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model. For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the
onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
at larger recoil angles. \\
\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
GeV$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 GeV$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig2}

@@

\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.

@@

\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)} and  \hyperref[fig:fig2]{2(b)},  all models predict similar behaviour of the

@@

\indent In Fig. \hyperref[fig:fig2]{2(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig2]{2(b)},
a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum dis-
\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the Paris(blue), AV18(green) and CD-Bonn(magenta) theoretical reduced cross sections.}
\label{fig:fig2}
\end{center} \\
%Begin text ON NEW PAGE after FIGURE 2. If Figure 2 changed position, move text from previous page (top) to this page (bottom)
\noindent tributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.

@@

\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
%while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
%experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
%of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c.
The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
behavior that was not predicted by any of the models. \\
\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.

%We conclude that these results although very interesting, does not have the sufficient statistics and the
%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\

%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

>>>>

A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the SHMS and the High Momentum Spectrometer (HMS), respectively. The ``missing'' (undetected) neutron was reconstructed from energy-momentum conservation laws:
$\vec{p_{r}} = \vec{q} - \vec{p_{f}}$ (missing momentum) and $E_{m} = \omega - T_{p} - T_{r}$ (missing energy), where $\vec{p_{f}}$ is the final proton momentum, $(T_{p}, T_{r})$ are the
final proton and neutron kinetic energies, and $E_{m}$ is the binding (missing) energy of the deuteron.
The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\

@@

\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) moved from smaller to larger angles corresponding the
the lower and higher missing momentum settings, respectively. At these kinematics, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$)
measured on this experiment. As a result one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
At these forward angles and large momentum transferred to the proton, the additional process in which the recoiling neutron is struck by the vitrual photon is suppressed. \\
\indent Hydrogen elastic ($^{1}H(e,e'p)$) data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
simulation program, SIMC. Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 
momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\
\indent Identical event selection criteria were used for the hydrogen and deuteron data. The criteria were determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
is well known, 2) a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, 3) a missing
energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a cut on the reconstructed HMS and SHMS reaction vertices to select events that truly

@@

\indent The experimental data yield for both hydrogen and deuteron data was normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS),
total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}. \\
\indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$. For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).
The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist. \\
\indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
Determination of systematics on these quantities is a work in progress. (Private communication with D. Mack)} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)

@@

\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins

@@

The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated. The ratio between the calculated cross section at the averaged kinematics and the averaged
cross section for this bin has also been determined and used to compare theoretical models to the experimental cross sections. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were 
\includegraphics[scale=0.45]{../prl_plots/PRL_plot1.pdf}
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
AV18(green) and CD-Bonn(magenta) NN potentials}
\end{center}
\noindent averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. \\
%--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
(GeV/c)$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig1}

@@

\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.

@@

\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the

@@

\indent In Fig. \hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig1]{1(a)}.

@@

%---------------------------------------------------------------------------------------------------------------------

%------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------

%\begin{figure}
%\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
%\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
%                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
%\label{fig:fig2}
%\end{figure}
%\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
%relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig. \ref{fig:fig2}. The theoretical calculations for the
%CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M. Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
%in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig2}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}],
%the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
%up to $\sim$ 800 MeV/c before being overwhelmed by FSIs. The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
%with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(b)}], both the data and
%CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
%a similar behaviour as in Fig. \hyperref[fig:fig2]{2(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model. For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], the
%onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
%at larger recoil angles. \\

%-------------------------------------------------------------------------------------------------------------------------------

%----------CONCLUSION----------

%\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
%unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
%The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
%up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
%behavior that was not predicted by any of the models. \\
%\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
%the original proposal\cite{e12_10_003_proposal}, we conclude that additional beam time is required to measure the full kinematic coverage as the results presented on this Letter
%(although very interesting) do not have the necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed. \\
%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
%to the equipment for the Hall C upgrade making all four commissioning experiments possible.

%-------------------------------

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/introduction.tex
updated

to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.

@@

decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. Both MECs and ICs in addition to FSIs can significantly alter the recoiling neutron

@@

%(1) The above-mentioned long-range processes alter the final neutron
%momentum making the deuteron momentum distributions difficult to access.\\
\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped constrain and quantify the contributions from FSIs, MECs and ICs on
the $^{2}H(e,e'p)n$ cross-section and determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs). The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
at a relatively low momentum transfer of $Q^{2}=0.665$ GeV$^{2}$ and neutron recoil momenta
up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}
for a satisfactory agreement between theory and data. \\
%(2) the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory
%agreement between the theory and data. \\

@@

the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 GeV$^{2}$) and presented angular distributions of cross-sections that confirmed the onset of
the General Eikonal Approximation (GEA)\cite{sargsian_2001,PhysRevC.56.1124}, which predicts a strong angular dependence of FSI with neutron recoil angles with a peak at $\theta_{nq} \sim 70^{o}$.
The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it impossible to select kinematical bins in $\theta_{nq}$ where
FSIs were small to extract momentum distributions.\\
% (3) The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated neutron recoil angles in the range $20^{o}< \theta_{nq}<160^{o}$
%to gain better statistical precision. As a result, it was not possible to choose kinematical regions binned in $\theta_{nq}$ in which FSI were minimal to extract the momentum distributions. \\
\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at published $Q^{2} = 3.5\pm0.25$ GeV$^{2}$ and recoil momenta up to 550 MeV/c. The angular distributions of
the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented verified the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil

@@

% (4) This kinematic window in which FSI are small can also be seen in the momentum distributions for
%$\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, where data and theory agree well within the PWIA kinematics.
\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measruements
to $Q^{2}=4.5\pm0.5$ GeV$^{2}$ and neutron recoil momenta up to 1.18 GeV/c. At these kinematics, MECs and ICs are suppressed and FSIs are under control for neutron recoil angles between 35 and 45 degrees

>>>>

to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\

@@

decays back into the ground state nucleon causing further re-scattering between the proton and neutron. Both MECs and ICs in addition to FSIs can significantly alter the recoiling neutron

@@

\indent Theoretically, MECs and ICs are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
The suppression of MECs can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ (GeV/c)$^{2}$ and
$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}. The ICs can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
electro-production threshold. \\
\indent For FSIs at large $Q^{2}$, the onset of the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} is expected which predicts a strong angular dependence of the FSIs with neutron recoil angles where FSI peaks at $\theta_{nq}\sim70^{o}$. The
most important prediction from GEA, however, is that at large recoil momenta $p_{r}$ where FSIs are expected to be large, there is an approximate cancellation of the PWIA/FSI interference (screening term) with the
modulus-squared of the FSI amplitude (rescattering term). This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$,
opening a kinematic window to study the short-range structure of the deuteron. \\
\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped confirmed various of the abovementioned theoretical predictions as well as constrain and quantify the contributions from FSIs, MECs and ICs on
the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs). The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
at a relatively low momentum transfer of $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs dominate the cross section and
had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214} for a satisfactory agreement between theory and data. \\

@@

the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$) and presented angular distributions of cross-sections that exhibited a strong angular dependence of FSI with neutron recoil angles peaking
at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}.
The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it necessary to integrate over a wide angular range making it impossible to control
contributions from FSIs, MECs and ICs. \\
\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at $Q^{2} = 3.5\pm0.25$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c. The angular distributions of
the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented confirmed the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil

@@

\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements
to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.18 GeV/c. At these kinematics, MECs and ICs are suppressed and FSIs are under control for neutron recoil angles between 35 and 45 degrees
